Data Management for LSST Special Programs

### 2023-05-20 sec_sci.tex
Update sec_sci.tex

Recommended implementation aspects for the requirements related to 
Special Programs (Section~\ref{sec:req}).

@@

Thus \textbf{all visits should have a region label \textit{and} a program 
label.}

@@

\textbf{Program Labels -- } based on survey cadeance or strategy.
Program labels might include, e.g., WFD, DDF, mini-survey name, or other 
options like engineering, commissioning, and director's discretionary.
Program labels should be propagated to all single-visit processed and 
difference images, and cataloged sources.

@@

The existence and propagation of these \textit{specific} labels is not a 
requirement.
This document suggests that these labels be the adopted implementation for 
the metadata requirements (see Section~\ref{ssec:req_meta}).

@@

As described in Section~\ref{ssec:proc_spdp} this processing capacity will be 
accessed via Rubin Science Platform, with a supported software environment and 
infrastructure for batch processing \citedsp{dmtn-202}.

>>>>

High-level recommendations regarding RDM implementations to meet the 
requirements related to Special Programs summarized in Section~\ref{sec:req}.

@@

\textbf{All visits should have a region label \textit{and} a program 
label, and these labels should be propagated to all processed images and catalog data.}

@@

\textbf{Program Labels -- } 
Should be based on survey cadeance or strategy.
Program labels might include, e.g., WFD, DDF, mini-survey name, or other 
options like engineering, commissioning, and director's discretionary.
Program labels should be propagated to all single-visit processed and 
difference images, and all cataloged sources.

@@

The existence and propagation of these labels is not a requirement.
This document suggests that these labels be the adopted implementation for 
the metadata requirements (see Section~\ref{ssec:req_meta}).

@@

As described in Section~\ref{ssec:proc_user} this processing capacity will be 
accessed via Rubin Science Platform, with a supported software environment and 
infrastructure for batch processing \citedsp{dmtn-202}.
